Potential Factors of Decreasing Birth Rates in the US since the Great Recession and Beyond

### 2024-02-09 outputs/paper/paper.qmd
Update paper.qmd

Age over 30

@@

From now on, every white refers to non-Hispanic, caucassian. Every black refers to non-Hispanic, African American. Hispanic refers to people with Hispanic ethinicity majority from south America.

@@

## Features

>>>>

@@

We replicate the paper by Kearney, Levine, and Pardue (2022) with a focus on the following research questions: 
- What is the trend in the US birth rates over the period 1980 to 2020?
- How does the birth rates vary by the age group?
- How does the birth rates vary by the race and ethnicity of mothers'?

The original code in the replication package is written in Stata. However, this paper utilizes R (R Core Team 2020) to analyze a dataset from the replication package. Packages such as ggplot2 (Wickham et al. 2016) for creating graphical representations, kableExtra (Zhu et al. 2021) for enhancing table aesthetics, and lubridate (Grolemund et al. 2021) for handling date-related operations were employed. Additionally, the Tidyverse framework (Wickham et al. 2019) ensures cohesiveness, while Dplyr (Wickham et al. 2021) facilitates data manipulation.

@@

## Features
From now on, every white refers to non-Hispanic, caucassian. Every black refers to non-Hispanic, African American. Hispanic refers to people with Hispanic ethinicity majority from south America.
